DisReserv (v1.0): Analytical displacement solution due to reservoir compaction with arbitrary geometry and under arbitrary pressure changes

### 2020-09-19 manuscript/manuscript-reservoir.tex
subsection 3.3

We parameterize the reservoir as a grid of juxtaposed right rectangular prisms.
Each grid prism has a constant pressure contrast $\Delta p_{j}$; however, pressure variations among different prisms are allowed. 
To calculate the displacement field produced by the $j$th prism
at the $i$th coordinates  $(x_i$, $y_i, z_i)$, we integrate the solution deduced for a single nucleus of strain (equation \ref{eq:displacement_ui})
over its volume and obtain
\begin{equation}
{\bf{\tilde{u}}}_{ij} = 
\iiint\limits_{{v_{1}}_{j}}
{\bf{u_{1}}}_{ij} \: \:  dv_{j}^{\prime}
\: + \:
\iiint\limits_{{v_{2}}_{j}}
{\bf{u_{2}}}_{ij} \:\:  dv_{j}^{\prime} \: ,
\label{eq:nucleus-ui_jth_prism}
\end{equation}
where both integrals are conducted with respect to the variables 
$(x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$. The first integral in equation 
\ref{eq:nucleus-ui_jth_prism} is conducted over the volume ${v_{1}}_{j}$ of the $j$th
prism and the second is conducted over the volume 
${v_{2}}_{j}$ of a different prism symmetrically positioned above the free surface 
and conveniently called $j$th "image prism".
Volume ${v_{1}}_{j}$ is defined by ${x_1}_{j}$, ${x_2}_{j}$, ${y_1}_{j}$, ${y_2}_{j}$,
${z_1}_{j}$, and ${z_2}_{j}$, which represent, respectively, the south, north, west, 
east, top, and bottom borders of the $j$th prism.
Volume ${v_{2}}_{j}$ of the $j$th image prism is defined in a similar way, but with 
top and bottom given by $z_1 - 2 \, z_c$ and $z_2 - 2 \, z_c$, where 
$z_c = \frac{1}{2}(z_1 + z_2)$ is the center depth of the $j$th prism.
By substituting equations \ref{eq:nucleus-u1-vector} and \ref{eq:nucleus-u2-vector} 
into equation \ref{eq:nucleus-ui_jth_prism}, we obtain
\begin{equation}
{\tilde{u}}_{{ij}_\alpha} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}} 
\frac{\partial }{\partial \alpha} {\frac{1}{{R_1}_{ij}}} \:  dv_{j}^{\prime} 
\: + \: 
(3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial \alpha} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_{j}^{\prime} 
\right] \: , 
\label{eq:u_til_alpha}
\end{equation}
where $\alpha = x, y$, and
\begin{equation}
{\tilde{u}}_{{ij}_z} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}}
\frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: - \: (3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial z} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j 
\right] \: .
\label{eq:u_til_z}
\end{equation}
In the right-hand side of equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}, the three integrals have the same form of derivatives of the gravitational potential produced by the 
$j$th prism. 
The first integral corresponds to the $\alpha-$component of the gravitational attraction 
produced by the $j$th prism.
The second and third integrals correspond, respectively, to the $\alpha-$component of the gravitational attraction and to the $\alpha \:z-$component of the gravitational 
gradient tensor produced by the $j$th image prism. 
The similarity between the displacement fields due to a volume source in a half-space and the gravitational field allows the use of closed expressions of the gravitational potential and its derivatives produced by the 3D right rectangular prism.

@@

\frac{\partial^{2}  }{\partial x \partial z} {\frac{1}{{R_2}_{ij}}}  dv_j = \Bigg|\Bigg|\Bigg| 

@@

\frac{\partial^{2}  }{\partial y \partial z} {\frac{1}{{R_2}_{ij}}}  dv_j =

@@

\ln(x + {R_2})

@@

\frac{\partial^{2}  }{\partial z \partial z} {\frac{1}{{R_2}_{ij}}}  dv_j =

@@

% Displacement produced by the whole reservoir 
Finally, the total displacement vector at the point $(x_i, y_i, z_i)$ due to the
pressure change in the whole reservoir is defined as the sum of the displacements 
${\bf{u}}_{ij}$ (equation \ref{eq:nucleus-ui_jth_prism}) yielded by each prism 
with constant pressure $\Delta p_{j}$:
\begin{equation}
{\bf{\tilde{u}}}_{i} = \sum_{j=1}^{M} {\bf{\tilde{u}}}_{ij} \: ,
\label{eq:nucleus-ui_M_prisms}
\end{equation}
where $M$ is the number of prisms setting up the reservoir model.
The horizontal component of the total displacement vector ${\bf{\tilde{u}}}_{i}$ 
(equation \ref{eq:nucleus-ui_M_prisms}) is calculated by 
\begin{equation}
{\tilde{u}}_{{i}_h} = \sqrt{ {\tilde{u}}_{{i}_x}^{2}  +  {\tilde{u}}_{{i}_y}^{2} } 
\: ,
\label{eq:horizontal_displacement}
\end{equation}
where ${\tilde{u}}_{{i}_x}$ and ${\tilde{u}}_{{i}_y}$ are the $x-$ and $y-$ components.

@@

By following the similar approach used in the displacement forward modeling due to a prism in a homogeneous elastic semi-infinite medium (subsection \ref{u-model}), the stress field of each prism assuming constant pressure is calculated by integrating over its volume the stress of a nucleus of strain located at its center. 
Next, the stresses due to a set of $M$ prisms modeling the reservoir is summed to yield the stress field  due to the pressure change in the whole reservoir.

Like equation \ref{eq:nucleus-ui_M_prisms}, the stress field at the $i$th coordinates ($x_i$, $y_i$  and $z_i$) due to the pressure change in the whole reservoir can be written as:
\begin{equation}
\tilde{\mbox{\boldmath$\sigma$}}_{i}(x_i,y_i,z_i)
= \sum_{j=1}^{M} 
\int_{z_1}^{z_2} \:\:
\int_{y_1}^{y_2} \:\: 
\int_{x_1}^{x_2} 
\mbox{\boldmath$\sigma_{1}$}_{i}\: \:  dx^{\prime}_j dy^{\prime}_j dz^{\prime}_j 
\: + \: 
\int_{z_1}^{z_2} \:\:
\int_{y_1}^{y_2} \:\: 
\int_{x_1}^{x_2} 
\mbox{\boldmath$\sigma_{2}$}_{i} \:\:  dx^{\prime}_j dy^{\prime}_j dz^{\prime}_j, 
\label{eq:nucleus-stress_M_prisms}
\end{equation}
where the limits of the integrals represent the borders of the $j$th prism modeling the reservoir in the following way: $x_1$ and $x_2$ are their south and north borders; $y_1$ and  $y_2$ are their  west and east borders;  and $z_1$ and $z_2$ are their depths to the top and bottom.

From equations \ref{eq:nucleus-stress1-vector} and \ref{eq:nucleus-stress2-vector}, we write, respectively,  the $\alpha-$component (where  $\alpha = x$ and $y$) and the $z-$ component of the stress field at the $i$th coordinates ($x_i$, $y_i$  and $z_i$) due to the pressure change in the whole reservoir, i.e.:
\begin{equation}
{\tilde{\sigma}}_{{i}_\alpha} = A \: \sum_{j=1}^{M} 
\: \Delta p_{j}  \: \int\int\limits_{v_j}\int 
\frac{\partial^{2}}{\partial \alpha \partial z} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: +   \int\int\limits_{v_j}\int
\: \frac{\partial^{2} }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \int\int\limits_{v_j}\int
\frac{\partial^{3}  }{\partial \alpha \partial z ^{2}} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j, 
\label{eq:stress_til_alpha}
\end{equation}
and 
\begin{equation}
{\tilde{\sigma}}_{{i}_z} = A \: \sum_{j=1}^{M} 
\: \Delta p_{j}  \: \int\int\limits_{v_j}\int 
\frac{\partial^{2}}{\partial z^{2}} {\frac{1}{{R_1}_{ij}}} \:  dv_j 
\: -   \int\int\limits_{v_j}\int
\: \frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \int\int\limits_{v_j}\int
\frac{\partial^{3}  }{\partial z ^{3}} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_j, 
\label{eq:stress_til_z}
\end{equation}
where $dv_j$ is the $j$th element of volume of the $j$th prism whose volume is $v_j$.

Like in the displacement field (equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}), the three integrals, in the right-hand side of equations \ref{eq:stress_til_alpha} and \ref{eq:stress_til_z}, are equal to  quantities of the gravitational attraction produced by the $j$th prism considering that $\Delta p_{j}$ is the density of the $j$th prism and the constants are equivalent to the gravitational constant. 
In equation \ref{eq:stress_til_alpha}, the first and second integrals correspond to the $\alpha \:z-$component of the gravity gradient tensor (where  $\alpha = x$ and $y$) produced, respectively, by the $j$th prism and $j$th image nucleus; and the third integral corresponds to the first derivative with respect to $\alpha$ of the $zz-$component of the gravity gradient tensor produced by the $j$th image nucleus. 
In equation \ref{eq:stress_til_z}, the first and second integrals correspond to the $zz-$component of the gravity gradient tensor produced, respectively, by the $j$th prism and $j$th image nucleus; and the third integral corresponds to the first derivative with respect to $z$ of the $zz-$component of the gravity gradient tensor produced by the $j$th image nucleus.

Here, we also use the closed expressions of the gravitational potential and its derivatives produced by the 3D right rectangular prism derived by \cite{Nagyetal2000} and (\citeyear{Nagyetal2002}) to calculate the stress field due to a volume source in a half-space.  
The first integral in equations  \ref{eq:stress_til_alpha} and \ref{eq:stress_til_z}
corresponds, respectively, to the $\alpha \:z-$ and $zz-$components of the gravity gradient tensor produced by the $j$th prism modeling the reservoir.
These second partial derivatives of ${\frac{1}{{R_1}_{ij}}}$ with respect to $xz$, $yz$ and $zz$ are calculated using the analytical expressions given by equations \ref{dx2} $-$ \ref{dz2} but substituting 
$\frac{1}{{R_2}_{ij}} \equiv \frac{1}{R_2}$ by 
$\frac{1}{{R_1}_{ij}} \equiv \frac{1}{R_1}$.

The second and third integrals in the right-hand side of  equations  \ref{eq:stress_til_alpha}  and \ref{eq:stress_til_z} are related with the correction of the stresses considering  a semi-space (image nucleus solution).
These integrals depend on the distance ${R_2}_{ij}$ from the $i$th coordinate point of the stress to the $j$th image nucleus, where the variable $z$ is given by the equations \ref{z_image} and \ref{z_c}.
In the right-hand side of  equations  \ref{eq:stress_til_alpha} and \ref{eq:stress_til_z}, 
the second integral is the second partial derivatives of ${\frac{1}{{R_2}_{ij}}}$ with respect to $xz$, $yz$ and $zz$ given by equations  \ref{dx2} $-$ \ref{dz2} and the third integral is the third partial derivatives of ${\frac{1}{{R_2}_{ij}}}$ with respect to $xzz$, $yzz$ and $zzz$ given by (\cite{Nagyetal2000}):
\begin{equation}
\int\int\limits_{v_j}\int 
\frac{\partial^{3}}{\partial x \partial z^{2}} {\frac{1}{{R_2}_{ij}}}  dv_j =
\Bigg|\Bigg|\Bigg| 
\frac{- y z}{R_2} \Big( \frac{1}{x^{2} + z^{2}} \Big)
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{sx3}
\end{equation}
\begin{equation}
\int\int\limits_{v_j}\int  
\frac{\partial^{2}  }{\partial y \partial z^{2}} {\frac{1}{{R_2}_{ij}}}  dv_j =
\Bigg|\Bigg|\Bigg|
\frac{- x z}{R_2} \Big( \frac{1}{y^{2} + z^{2}} \Big)
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{sy3}
\end{equation}
\begin{equation}
\int\int\limits_{v_j}\int 
\frac{\partial^{3}  }{\partial z^{3}} {\frac{1}{{R_2}_{ij}}}  dv_j =
\Bigg|\Bigg|\Bigg|
\frac{ x y}{R_2} \Big( \frac{1}{x^{2} + z^{2}} + \frac{1}{y^{2} + z^{2}} \Big)
\Bigg|_{x_1}^{x_2} \Bigg|_{y_1}^{y_2} \Bigg|_{z_1}^{z_2}
\label{sz3}
\end{equation}

>>>>

We parameterize the reservoir as a grid of juxtaposed right rectangular prisms.
Each grid prism has a constant pressure contrast $\Delta p_{j}$; however, pressure variations among different prisms are allowed. 
To calculate the displacement field produced by the $j$th prism
at the $i$th coordinates  $(x_i, y_i, z_i)$, we integrate the solution deduced for a single nucleus of strain (equation \ref{eq:displacement_ui})
over its volume and obtain
\begin{equation}
{\bf{\tilde{u}}}_{ij} = 
\iiint\limits_{{v_{1}}_{j}}
{\bf{u_{1}}}_{ij} \: \:  dv_{j}^{\prime}
\: + \:
\iiint\limits_{{v_{2}}_{j}}
{\bf{u_{2}}}_{ij} \:\:  dv_{j}^{\prime} \: ,
\label{eq:nucleus-ui_jth_prism}
\end{equation}
where both integrals are conducted with respect to the variables 
$(x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$. The first integral in equation 
\ref{eq:nucleus-ui_jth_prism} is conducted over the volume ${v_{1}}_{j}$ of the $j$th
prism and the second is conducted over the volume 
${v_{2}}_{j}$ of a different prism symmetrically positioned above the free surface 
and conveniently called $j$th "image prism".
Volume ${v_{1}}_{j}$ is defined by ${x_1}_{j}$, ${x_2}_{j}$, ${y_1}_{j}$, ${y_2}_{j}$,
${z_1}_{j}$, and ${z_2}_{j}$, which represent, respectively, the south, north, west, 
east, top, and bottom borders of the $j$th prism.
Volume ${v_{2}}_{j}$ of the $j$th image prism is defined in a similar way, but with 
top and bottom given by $z_1 - 2 \, z_c$ and $z_2 - 2 \, z_c$, where 
$z_c = \frac{1}{2}(z_1 + z_2)$ is the center depth of the $j$th prism.

The total displacement vector at the point $(x_i, y_i, z_i)$ due to the
pressure change in the whole reservoir is defined as the sum of the displacements 
${\bf{u}}_{ij}$ (equation \ref{eq:nucleus-ui_jth_prism}) yielded by each prism 
with constant pressure $\Delta p_{j}$:
\begin{equation}
{\bf{\tilde{u}}}_{i} = \sum_{j=1}^{M} {\bf{\tilde{u}}}_{ij} \: ,
\label{eq:nucleus-ui_M_prisms}
\end{equation}
where $M$ is the number of prisms setting up the reservoir model.
The horizontal component of the total displacement vector ${\bf{\tilde{u}}}_{i}$ 
(equation \ref{eq:nucleus-ui_M_prisms}) is calculated by 
\begin{equation}
{\tilde{u}}_{{i}_h} = \sqrt{ {\tilde{u}}_{{i}_x}^{2}  +  {\tilde{u}}_{{i}_y}^{2} } 
\: ,
\label{eq:horizontal_displacement}
\end{equation}
where ${\tilde{u}}_{{i}_x}$ and ${\tilde{u}}_{{i}_y}$ are the $x-$ and $y-$ components.

By substituting equations \ref{eq:nucleus-u1-vector} and \ref{eq:nucleus-u2-vector} 
into equation \ref{eq:nucleus-ui_jth_prism}, we obtain
\begin{equation}
{\tilde{u}}_{{ij}_\alpha} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}} 
\frac{\partial }{\partial \alpha} {\frac{1}{{R_1}_{ij}}} \:  dv_{j}^{\prime} 
\: + \: 
(3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial \alpha} {\frac{1}{{R_2}_{ij}}}\:  dv_j
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}}  \:\:  dv_{j}^{\prime} 
\right] \: , 
\label{eq:u_til_alpha}
\end{equation}
where $\alpha = x, y$, and
\begin{equation}
{\tilde{u}}_{{ij}_z} = \frac{A  \: (1 + \nu)}{E} 
\: \Delta p_{j}  \: \left[ \iiint\limits_{{v_{1}}_{j}}
\frac{\partial }{\partial z} {\frac{1}{{R_1}_{ij}}} \: dv_{j}^{\prime} 
\: - \: (3  - 4 \nu)  \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial }{\partial z} {\frac{1}{{R_2}_{ij}}}\: dv_{j}^{\prime}
+ \: 2 \: z_{i} \:  \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{2}  }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}}  \:\: dv_{j}^{\prime} 
\right] \: .
\label{eq:u_til_z}
\end{equation}
In the right-hand side of equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}, the three integrals have the same form of derivatives of the gravitational potential produced by the $j$th prism and image prism. 
The first integral corresponds to the $\alpha-$component of the gravitational attraction 
produced by the $j$th prism.
The second and third integrals correspond, respectively, to the $\alpha-$component of the gravitational attraction and to the $\alpha \:z-$component of the gravitational 
gradient tensor produced by the $j$th image prism. 
The similarity between the displacement fields due to a volume source in a half-space and the gravitational field allows the use of closed expressions of the gravitational potential and its derivatives produced by the 3D right rectangular prism.

@@

\frac{\partial^{2}  }{\partial x \partial z} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} = \Bigg|\Bigg|\Bigg| 

@@

\frac{\partial^{2}  }{\partial y \partial z} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} =

@@

\ln(x + R)

@@

\frac{\partial^{2}  }{\partial z \partial z} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} =

@@

@@

By following the similar approach used in the previous subsection, the stress field of each prism assuming constant pressure is calculated by integrating solution for a 
nucleus of strain (equations \ref{eq:stress_nucleus}, \ref{eq:nucleus-stress1-vector},
and \ref{eq:nucleus-stress2-vector}) over its volume. 
This integration leads to a stress vector 
$\mbox{\boldmath$\tilde{\sigma}$}_{ij} \equiv \mbox{\boldmath$\tilde{\sigma}$}(x_{i}, y_{i}, z_{i}, x^{\prime}_{j}, y^{\prime}_{j}, z^{\prime}_{j})$ given by
\begin{equation}
\mbox{\boldmath$\tilde{\sigma}$}_{ij} = 
\iiint\limits_{{v_{1}}_{j}}
\mbox{\boldmath$\sigma_{1}$}_{ij} \: \:  dv_{j}^{\prime}
\: + \:
\iiint\limits_{{v_{2}}_{j}}
\mbox{\boldmath$\sigma_{2}$}_{ij} \:\:  dv_{j}^{\prime} \: ,
\label{eq:nucleus-stress_jth_prism}
\end{equation}
where the first and second integrals are conducted, respectively, over the volumes 
${v_{1}}_{j}$ and ${v_{2}}_{j}$ of the $j$th prism and the $j$th image prism.
The total stress vector at the $i$th coordinates  $(x_i, y_i, z_i)$ due to the 
pressure change in the whole reservoir is calculated by 
\begin{equation}
\mbox{\boldmath$\tilde{\sigma}$}_{i} = 
\sum_{j=1}^{M} \mbox{\boldmath$\tilde{\sigma}$}_{ij} \: .
\label{eq:nucleus-stress_M_prisms}
\end{equation}

By substituting equation \ref{eq:nucleus-stress1-vector} and 
\ref{eq:nucleus-stress2-vector} into equation \ref{eq:nucleus-stress_jth_prism}, 
we obtain the $\alpha-$component (where  $\alpha = x$ and $y$) and the $z-$ component 
of the stress vector $\mbox{\boldmath$\tilde{\sigma}$}_{ij}$ as follows:
\begin{equation}
{\tilde{\sigma}}_{{ij}_\alpha} = A \: \Delta p_{j} \: \left[
\iiint\limits_{{v_{1}}_{j}}
\frac{\partial^{2}}{\partial \alpha \partial z} {\frac{1}{{R_1}_{ij}}} \: dv_{j}^{\prime}
\: + \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial^{2} }{\partial \alpha \partial z} {\frac{1}{{R_2}_{ij}}} \: 
dv_{j}^{\prime}
+ \: 2 \: z_{i} \: \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{3}  }{\partial \alpha \partial z ^{2}} {\frac{1}{{R_2}_{ij}}}  \:\: 
dv_{j}^{\prime} \right]
\label{eq:stress_til_alpha}
\end{equation}
and 
\begin{equation}
{\tilde{\sigma}}_{{ij}_{z}} = A \: \Delta p_{j} \: \left[
\iiint\limits_{{v_{1}}_{j}}
\frac{\partial^{2}}{\partial z^{2}} {\frac{1}{{R_1}_{ij}}} \: dv_{j}^{\prime}
\: + \iiint\limits_{{v_{2}}_{j}}
\: \frac{\partial^{2} }{\partial z^{2}} {\frac{1}{{R_2}_{ij}}} \: 
dv_{j}^{\prime}
+ \: 2 \: z_{i} \: \iiint\limits_{{v_{2}}_{j}}
\frac{\partial^{3}  }{\partial z^{3}} {\frac{1}{{R_2}_{ij}}}  \:\: 
dv_{j}^{\prime} \right] \: .
\label{eq:stress_til_z}
\end{equation}

Similarly to the displacement field (equations \ref{eq:u_til_alpha} and \ref{eq:u_til_z}), the three integrals in the right-hand side of equations \ref{eq:stress_til_alpha} and \ref{eq:stress_til_z} have the same form of 
derivatives of the gravitational potential produced by the $j$th prism and image prism.
The integrals depending on $\frac{1}{{R_1}_{ij}}$ have the following closed 
solutions \citep{Nagyetal2000, Nagyetal2002}:
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial^{2}  }{\partial x \partial z} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} = \Bigg|\Bigg|\Bigg| 
\ln(y + R)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dxz1}
\end{equation}
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial^{2}  }{\partial y \partial z} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
\ln(x + R)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dyz1}
\end{equation}
and
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j}}^{{z_{2}}_{j}}
\frac{\partial^{2}  }{\partial z \partial z} {\frac{1}{{R_1}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
-   \tan^{-1} \Bigg( \frac{xy}{z \: R} \Bigg)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{dzz1}
\end{equation}
where the limits ${X_1}_{j}$, ${X_2}_{j}$, ${Y_1}_{j}$, ${Y_2}_{j}$, ${Z_1}_{j}$, and ${Z_2}_{j}$ are defined by equation \ref{eq:Nagy_limits_1}.
The integrals depending on second derivatives of $\frac{1}{{R_2}_{ij}}$ in the 
right-hand side of equations \ref{eq:stress_til_alpha} and \ref{eq:stress_til_z} 
have closed solutions defined by equations \ref{dxz2}, \ref{dyz2}, and \ref{dzz2}.
Finally, the remaining integrals depending on third derivatives of 
$\frac{1}{{R_2}_{ij}}$ have closed solutions given by 
\citep{Nagyetal2000, Nagyetal2002}:
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j} - 2 \, z_c}^{{z_{2}}_{j} - 2 \, z_c}
\frac{\partial^{3}}{\partial x \partial z^{2}} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg| 
\frac{- y z}{R} 
\left( \frac{1}{x^{2} + z^{2}} \right)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{sxzz}
\end{equation}
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j} - 2 \, z_c}^{{z_{2}}_{j} - 2 \, z_c}
\frac{\partial^{2}  }{\partial y \partial z^{2}} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
\frac{- x z}{R} 
\left( \frac{1}{y^{2} + z^{2}} \right)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{syzz}
\end{equation}
\begin{equation}
\int\limits_{{x_{1}}_{j}}^{{x_{2}}_{j}} \int\limits_{{y_{1}}_{j}}^{{y_{2}}_{j}} \int\limits_{{z_{1}}_{j} - 2 \, z_c}^{{z_{2}}_{j} - 2 \, z_c}
\frac{\partial^{3}  }{\partial z^{3}} {\frac{1}{{R_2}_{ij}}} dv_{j}^{\prime} =
\Bigg|\Bigg|\Bigg|
\frac{ x y}{R} 
\left( \frac{1}{x^{2} + z^{2}} + \frac{1}{y^{2} + z^{2}} \right)
\Bigg|_{{X_1}_{j}}^{{X_2}_{j}} \Bigg|_{{Y_1}_{j}}^{{Y_2}_{j}} \Bigg|_{{Z_1}_{j}}^{{Z_2}_{j}} \quad ,
\label{sz3}
\end{equation}
where the limits ${X_1}_{j}$, ${X_2}_{j}$, ${Y_1}_{j}$, and ${Y_2}_{j}$, are defined 
by equation \ref{eq:Nagy_limits_1} and the limits ${Z_1}_{j}$, and ${Z_2}_{j}$ by
equation \ref{eq:Nagy_limits_2}.
